First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/body.tex
updated prl

one can infer that most of the virtual photon momentum is transferred to the proton. This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the

@@

the measured cross sections were compared to the model cross sections (incorporated as a SIMC subroutine) from calculations by J.M. Laget using the Paris potential. Variations

@@

This agreement gives us confidence on the measurements made at higher missing momentum setting for which no data exists. \\

@@

to the statiscial uncertainty to obtain the final uncertainty in the cross section. \\

@@

relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig1}. The theoretical calculations for the
CD-Bonn and Argonne $v_{18}$\cite{PhysRevC.51.38} (AV18) potentials were performed by M. Sargsian and those for the Paris potential were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is

@@

\indent Figure \ref{fig:fig2} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum, $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
(GeV/c)$^{2}$. The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 (GeV/c)$^{2}$.  The overlay of the Hall A data (cyan) in Fig. \ref{fig:fig2}

@@

smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions. This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{PhysRevC.56.1124,Sargsian_2001} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.

@@

a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start 

@@

\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}

@@

\noindent to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig2]{2(a)}.

@@

\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days) of beam time and 3 out of the 8 kinematic settings approved in

@@

It would be highly desireable to perform the full experiment

>>>>

one can infer that most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$, $\theta_{pq}\sim 0$. This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the

@@

the measured cross sections were compared to the model cross sections (incorporated as a SIMC subroutine) from calculations by J.M. Laget using the Paris potential\cite{PhysRevC.21.861}. Variations

@@

This agreement gives us confidence on the measurements made at higher missing momentum setting for which no previous data exists. \\

@@

to the statiscial uncertainty(25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\

@@

relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001} potential is shown in Fig. \ref{fig:fig1}. The theoretical calculations for the
CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} potentials were performed by M. Sargsian and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is

@@

\indent Figure \ref{fig:fig2} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
GeV$^{2}$. The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 GeV$^{2}$.  The overlay of the Hall A data (cyan) in Fig. \ref{fig:fig2}

@@

smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions. This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.

@@

a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum dis-

@@

\caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment (cyan) results\cite{PhysRevLett.107.262501} as well as the Paris(blue), AV18(green) and CD-Bonn(magenta) theoretical reduced cross sections.}

@@

\noindent tributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig2]{2(a)}.

@@

\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in

@@

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/prl.tex
updated prl

\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 GeV$^{2}$ and
  neutron recoil momenta up to $p_{r}\sim$1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the in-plane neutron recoil
  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA)
  dominates and comparison to recent theoretical calculations show data to be sensitive to momentum distributions up to $p_{r}\sim$ 700 MeV/c.

>>>>

\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 GeV$^{2}$ and
  neutron recoil momenta up to $p_{r}\sim$1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the in-plane neutron recoil
  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA)
  dominates and comparison to recent theoretical calculations show data to be sensitive to momentum distributions up to $p_{r}\sim$ 750 MeV/c.
